Fast Hyperparameter Selection for Graph Kernels via Subsampling and\\Multiple Kernel Learning

### 2017-02-08 paper.tex
correzioni varie

\subsection{Multiple Kernel Learning}
\label{MKL}
MKL \cite{Gonen2011} is one of the most popular paradigms used to learn kernels in real world applications \cite{Bucak2014}. % Zien2007,Wang2015a,Sun
The kernels generated by these techniques are combinations of a prescribed set of basic kernels $\KK_1,...,\KK_R$ in the form:
$ \KK = \sum_{r=1}^R \eta_r \KK_r$ with $\eeta \in \{ \eeta : \eeta \succcurlyeq 0, \| \eeta \|_q = 1 \}$. The value $q$ being the kind of mean used, is typically fixed to $1$ or $2$.

>>>>

\subsection{Multiple Kernel Learning}
\label{MKL}
MKL \cite{Gonen2011} is one of the most popular paradigms in real world applications \cite{Bucak2014} used to learn kernels as a combination of different base kernels $\KK_1,...,\KK_R$. % Zien2007,Wang2015a,Sun
In literature exists several kernels combination mechanisms, we focused on the form:
$ \KK = \sum_{r=1}^R \eta_r \KK_r$ with $\eeta \in \{ \eeta : \eeta \succcurlyeq 0, \| \eeta \|_q = 1 \}$. The value $q$ being the kind of mean used, is typically fixed to $1$ or $2$.
